Computational Methods for Principle Component Analysis Applied to Genotype Data

### 2018-06-20 doc/paper/paper.tex
Add fine-tuned plots to paper

\usepackage{epsfig} \usepackage[margin=1.5in]{geometry}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[capitalise]{cleveref}
\usepackage{verbatim}
\usepackage{float}
\usepackage{graphicx}

@@

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    \multicolumn{6}{|c|}{Study Runtime} \\
    \hline
    SP         &  17  & 17   & 16   & 18   & 18   \\
    AP         &  18  & 16   & 18  & 16   & 17  \\
    OADP       &  145  & 146   & 147   & 148   & 149   \\
    ADP        &  379  & 809 & 1526 & 2556 & 4062 \\
    \hline
    \multicolumn{6}{|c|}{Euclidean Error} \\
    \hline
    SP         &  188  & 139   & 112   & 91   & 84   \\
    AP         &  31  & 27   & 12  & 11   & 14  \\
    OADP       &  21  & 16   & 12   & 9   & 10   \\
    ADP        &  0  & 0 & 0 & 0 & 0 \\
    \hline
  \end{tabular}
  \caption{
    The runtimes and errors of the four methods
    as the reference size increases.
    Errors are measured as the Euclidean distance of
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
    }
\end{table}

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|r|r|r|}
    \hline
    Method & \multicolumn{2}{|c|}{Runtime} & \multicolumn{2}{|c|}{Error} \\
    & Global & European & Global & European \\
    \hline
    SP         &  62   & 48  &     & 450 \\ 
    AP         &  65   & 48  &     & 33  \\
    OADP       &  363  & 349 &     & 32  \\
    ADP        &  6745 & 518 &     & 0   \\
    \hline
  \end{tabular}
  \caption{
    The study runtimes (in seconds) and erros for the four methods
    for 500 randomly selected study samples
    in the UK Biobank data.
    Errors are measured as the Euclidean distance of
    the PC scores predicted by each method
    to those predicted by ADP.
    The 2492 samples from the 1000 Genomes data
    are used as the reference.
    The number of variants in common is 145,282.
    Only the top 4 PCs are calculated.
    }
\end{table}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ggsim_runtimes.png}
  \includegraphics[width=0.98\textwidth]{img/ggsim_errors.png}
  \caption{
    The runtimes (in seconds) and errors (Euclidean distance from ADP's PC scores) for the four methods
    as the reference size increases.
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
  }
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_sp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_ap}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_oadp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_adp}
  \caption{PC scores of 500 randomly selected global samples in UK Biobank data (circles) predicted by the four methods with the global samples in the 1000 Genomes data (squares) as the reference.}
\end{figure}

>>>>

\usepackage{epsfig}
\usepackage[margin=1in]{geometry}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage[capitalise]{cleveref}
\usepackage{verbatim}
\usepackage{float}
\usepackage{graphicx}
\usepackage{subcaption}

@@

\begin{figure}[p]
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1000_100000_200_2_1_100_1_sturef_ggsim1000_100000_1000_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1000_100000_200_2_1_100_1_sturef_ggsim1000_100000_1000_2_1_100_0_ap}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1000_100000_200_2_1_100_1_sturef_ggsim1000_100000_1000_2_1_100_0_oadp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1000_100000_200_2_1_100_1_sturef_ggsim1000_100000_1000_2_1_100_0_adp}
\end{subfigure}
\hfill
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1500_100000_200_2_1_100_1_sturef_ggsim1500_100000_1500_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1500_100000_200_2_1_100_1_sturef_ggsim1500_100000_1500_2_1_100_0_ap}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1500_100000_200_2_1_100_1_sturef_ggsim1500_100000_1500_2_1_100_0_oadp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim1500_100000_200_2_1_100_1_sturef_ggsim1500_100000_1500_2_1_100_0_adp}
\end{subfigure}
\hfill
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2000_100000_200_2_1_100_1_sturef_ggsim2000_100000_2000_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2000_100000_200_2_1_100_1_sturef_ggsim2000_100000_2000_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2000_100000_200_2_1_100_1_sturef_ggsim2000_100000_2000_2_1_100_0_oadp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2000_100000_200_2_1_100_1_sturef_ggsim2000_100000_2000_2_1_100_0_adp}
\end{subfigure}
\hfill
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2500_100000_200_2_1_100_1_sturef_ggsim2500_100000_2500_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2500_100000_200_2_1_100_1_sturef_ggsim2500_100000_2500_2_1_100_0_ap}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2500_100000_200_2_1_100_1_sturef_ggsim2500_100000_2500_2_1_100_0_oadp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim2500_100000_200_2_1_100_1_sturef_ggsim2500_100000_2500_2_1_100_0_adp}
\end{subfigure}
\hfill
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim3000_100000_200_2_1_100_1_sturef_ggsim3000_100000_3000_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim3000_100000_200_2_1_100_1_sturef_ggsim3000_100000_3000_2_1_100_0_sp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim3000_100000_200_2_1_100_1_sturef_ggsim3000_100000_3000_2_1_100_0_oadp}
\end{subfigure}%
\begin{subfigure}{.25\textwidth}
  \centering
  \includegraphics[width=.98\linewidth]{img/ggsim3000_100000_200_2_1_100_1_sturef_ggsim3000_100000_3000_2_1_100_0_adp}
\end{subfigure}
\caption{
  The PC scores predicted by each of the four methods
  as the reference size varies.
  Reference samples are in colors
  and study samples are in black.
  The number of variants is 100,000,
  and the study sample size is 200.
  Only the top 4 PCs are calculated.
  The data is simulated by the GGS software \citep{mathieson2012differential}.
}
\end{figure}

@@

\begin{table}[h]
  \centering
  \begin{tabular}{|l|l|l|l|l|l|}
    \hline
    Reference Size & 1000 & 1500 & 2000 & 2500 & 3000 \\
    \hline
    \multicolumn{6}{|c|}{Study Runtime} \\
    \hline
    SP         &  17  & 17   & 16   & 18   & 18   \\
    AP         &  18  & 16   & 18  & 16   & 17  \\
    OADP       &  145  & 146   & 147   & 148   & 149   \\
    ADP        &  379  & 809 & 1526 & 2556 & 4062 \\
    \hline
    \multicolumn{6}{|c|}{Error form ADP} \\
    \hline
    SP         &  188  & 139   & 112   & 91   & 84   \\
    AP         &  31  & 27   & 12  & 11   & 14  \\
    OADP       &  21  & 16   & 12   & 9   & 10   \\
    ADP        &  0  & 0 & 0 & 0 & 0 \\
    \hline
  \end{tabular}
  \caption{
    The runtimes and errors of the four methods
    as the reference size increases.
    Errors are measured as the Euclidean distance of
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
    }
\end{table}

\begin{figure}[h]

  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=.98\linewidth]{img/ggsim_runtimes.png}
  \end{subfigure}
  \begin{subfigure}{.5\textwidth}
    \centering
    \includegraphics[width=.98\linewidth]{img/ggsim_errors.png}
  \end{subfigure}
  \caption{
    The runtimes (in seconds) and errors (Euclidean distance from ADP's PC scores) for the four methods
    as the reference size increases.
    The number of variants is 100,000,
    and the study sample size is 200.
    Only the top 4 PCs are calculated.
    The data is simulated by the GGS software \citep{mathieson2012differential}.
  }
\end{figure}

\begin{table}[h]
  \centering
  \begin{tabular}{|r|r|r|r|r|}
    \hline
    Method & \multicolumn{2}{|c|}{Runtime} & \multicolumn{2}{|c|}{Error} \\
    \hline
    & Global & European & Global & European \\
    \hline
    SP         &  62   & 48  & 92  & 450 \\ 
    AP         &  65   & 48  & 48  & 33  \\
    OADP       &  363  & 349 & 10  & 32  \\
    ADP        &  6739 & 518 & 0   & 0   \\
    \hline
  \end{tabular}
  \caption{
    The study runtimes (in seconds) and erros for the four methods
    for 500 randomly selected study samples
    in the UK Biobank data.
    Errors are measured as the Euclidean distance of
    the PC scores predicted by each method
    to those predicted by ADP.
    The 2492 samples from the 1000 Genomes data
    are used as the reference.
    The number of variants in common is 145,282.
    Only the top 4 PCs are calculated.
    }
\end{table}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_sp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_ap}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_oadp}
  \includegraphics[width=0.98\textwidth]{img/ukb_snpscap_kgn_bial_orphans_5c_sturef_kgn_bial_orphans_snps_ukb_snpscap_ukb_adp}
  \caption{PC scores of 500 randomly selected global samples in UK Biobank data (circles) predicted by the four methods with the global samples in the 1000 Genomes data (squares) as the reference.}
\end{figure}
